---
title: "correlaid-utils"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This repository contains utility tools for CorrelAid.

:warning: Code in mailchimp-welcomemail is very outdated! Code was developed by [Frie](https://github.com/friep) back in 2017 but has not been actively used / maintained since 2018. The repository was solely open sourced for the purpose of Frie's talk at the [Open Online Data Meetup](https://www.eventbrite.com/e/the-lazy-data-scientist-automating-things-feat-r-python-aws-and-a-pi-registration-121498787143). Code in `correlaid-analytics` has been updated for a talk in November 2020 but please still proceed with caution :warning: 

Relevant older versions of this repository: 
- [correlaid-analytics Python / Serverless version](https://github.com/friep/correlaid-utils/releases/tag/serverless-python)
- [correlaid-analytics old R version](https://github.com/friep/correlaid-utils/releases/tag/rstats-old)


## correlaid-analytics
Code to get twitter follower, facebook likes, newsletter subscriber count and general network data on a daily basis using [{smcounts}](https://github.com/friep/smcounts). 

### Plots
_last updated_: `r Sys.time()`


```{r plot-alltime, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggiraph)
data <- readr::read_csv("correlaid-analytics/data/all_daily.csv")
ggplot(data = data) +
  geom_point_interactive(aes(x = date, y = n, color = platform,
  tooltip = n, data_id = date), size = 0.5)+
  labs(title = "CorrelAid platforms over time", caption = "No data was collected between end of 2017 and autumn 2020", x = "")+
  theme_minimal()
```


```{r plot2020, echo=FALSE, message=FALSE}
ggplot(data = data %>% dplyr::filter(date > "2020-01-01")) +
    geom_point_interactive(aes(x = date, y = n, color = platform,
    tooltip = n, data_id = date), size = 0.5) +
  geom_line_interactive(aes(x = date, y = n, color = platform,
    tooltip = n, data_id = date), size = 0.5)+
  facet_wrap(~platform, ncol = 2, scales = "free_y")+
  labs(title = "CorrelAid platforms over time", subtitle = "Only 2020 onwards, free y axes", x = "")+
  theme_minimal()

```

### Read the data 

```r
ca_counts <- readr::read_csv("https://raw.githubusercontent.com/friep/correlaid-utils/main/correlaid-analytics/data/all_daily.csv")
```

### Deployment on Raspberry Pi
```
install.packages("bspm")
bspm::enable()
install.packages("remotes")
install.packages("cronR")
install.packages("gert") # requires libssl-dev and libgit2-dev (install with sudo apt install)
```

1. install [{smcounts}](https://github.com/friep/smcounts) and its dependencies
2. copy `.Renviron` with all necessary environment variables and the `.slackr` file to the `correlaid-analytics` folder on the Raspberry Pi.
3. Copy `rtweet_token.rds` to home directory on Raspberry Pi (set `TWITTER_PAT` accordingly in .Renviron)
4. Run `cron.R` to set up cron job: `Rscript path/to/cron.R`. Check with `crontab -l`
5. add a `GITHUB_PAT` (GitHub Personal Access Token) to `.Renviron`. This is needed for the authentication with GitHub.

### GitHub Action
Every morning at 7am, GitHub Actions run to see whether a commit was made to the `all_daily.csv` file. If not, then the build fails and I'll get notified via email about the failed pipeline. 

## mailchimp-welcomemail (:warning: deprecated!)
This folder contains the code to automatically send out the welcome email to new subscribers to our newsletter once a day. 

### How does it work?
All the code resides on a raspberry pi which is located in @friep's flat. The individual steps are all wrapped in a bash file (runscripts.sh) that executes the scripts in their order. This bash file itself is scheduled to run each night on the raspberry pi using cronjobs. 

The scripts are in the order they are executed by runscripts.sh: 

1. get_new_subs.R: query the Mailchimp API for our newsletter subscriber list and write newly subscribed users to a temporary csv file.
2. send_mails.py: read in the temporary file and send out mails to the newly subscribed users by connecting to our mail server.
3. send_logs.py: send log files to @friep's correlaid address.